---
title: "Graph code"
author: "EK Mallott"
date: "2022-09-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

This is code for the graphs for Mallott 2022 in Proc B.

## Workspace setup

The following packages are used for this analysis:
tidyverse 1.3.2

```{r packages}
library(tidyverse)
library(ggarchery)
```

## Panel A

Individualized gut microbiomes with a time dependent environmental response.

### Set up dataframes

Create two tibbles - one for the points and one for the arrows.

```{r df_a}
points_a = tibble(Individual = c("A", "A", "A", "A", "B", "B", 
                                 "B", "B", "C", "C", "C", "C"), 
                  Timepoint = c("1", "2", "3", "4", "1", "2", 
                                "3", "4", "1", "2", "3", "4"),
                  X = c(0.2, 0.45, 0.45, 0.225, 0.35, 0.6, 0.6, 0.375,
                        0.55, 0.8, 0.8, 0.575),
                  Y = c(0.2, 0.35, 0.15, 0.1, 0.75, 0.9, 0.7, 0.65,
                        0.4, 0.55, 0.35, 0.3))
arrows_a = tibble(Individual = c("A", "A", "A", "B", "B", "B", "C", "C", "C"),
                  xstart = c(0.2, 0.45, 0.45, 0.35, 0.6, 0.6, 
                             0.55, 0.8, 0.8),
                  xend = c(0.45, 0.45, 0.225, 0.6, 0.6, 0.375, 
                           0.8, 0.8, 0.575),
                  ystart = c(0.2, 0.35, 0.15, 0.75, 0.9, 0.7, 0.4, 0.55, 0.35),
                  yend = c(0.35, 0.15, 0.1, 0.9, 0.7, 0.65, 0.55, 0.35, 0.3))
```

Create a scatterplot with arrows connecting points within the same individual. Color denotes individual and shape denotes timepoint.

```{r panel_a}
panel_A = ggplot(points_a) + 
  geom_point(aes(x = X, y = Y, color = Individual, shape = Timepoint), 
             size = 3) +
  scale_color_manual(values = c("#1ec93e", "#008ec8", "#4e3182")) +
  scale_shape_manual(values = c(15, 16, 17, 18)) +
  geom_segment(data = arrows_a, 
               aes(x = xstart, xend = xend, y = ystart, yend = yend,
                   color = Individual), 
               arrow = arrow(angle = 20),
               position = position_attractsegment(start_shave = 0.15, 
                                                  end_shave = 0.15)) +
  xlim(c(0, 1)) +
  ylim(c(0, 1)) +
  theme_classic() + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=rel(1)),
        axis.title.x=element_blank(), 
        axis.text.x=element_text(size=rel(1)))
panel_A
```

## Panel B

Individualized gut microbiomes without a time dependent environmental response.

### Set up dataframes

Create two tibbles - one for the points and one for the arrows.

```{r df_b}
points_b = tibble(Individual = c("A", "A", "A", "A", "B", "B", 
                                 "B", "B", "C", "C", "C", "C"), 
                  Timepoint = c("1", "2", "3", "4", "1", "2", 
                                "3", "4", "1", "2", "3", "4"),
                  X = c(0.2, 0.225, 0.45, 0.45, 0.35, 0.6, 0.375, 0.6,
                        0.55, 0.8, 0.8, 0.575),
                  Y = c(0.2, 0.1, 0.15, 0.35, 0.75, 0.7, 0.65, 0.9, 
                        0.4, 0.55, 0.35, 0.3))
arrows_b = tibble(Individual = c("A", "A", "A", "B", "B", "B", "C", "C", "C"),
                  xstart = c(0.2, 0.225, 0.45, 0.35, 0.6, 0.375, 
                             0.55, 0.8, 0.8),
                  xend = c(0.225, 0.45, 0.45, 0.6, 0.375, 0.6, 
                           0.8, 0.8, 0.575),
                  ystart = c(0.2, 0.1, 0.15, 0.75, 0.7, 0.65, 0.4, 0.55, 0.35),
                  yend = c(0.1, 0.15, 0.35, 0.7, 0.65, 0.9, 0.55, 0.35, 0.3))
```

Create a scatterplot with arrows connecting points within the same individual. Color denotes individual and shape denotes timepoint.

```{r panel_b}
panel_B = ggplot(points_b) + 
  geom_point(aes(x = X, y = Y, color = Individual, shape = Timepoint), 
             size = 3) +
  scale_color_manual(values = c("#1ec93e", "#008ec8", "#4e3182")) +
  scale_shape_manual(values = c(15, 16, 17, 18)) +
  geom_segment(data = arrows_b, 
               aes(x = xstart, xend = xend, y = ystart, yend = yend,
                   color = Individual), 
               arrow = arrow(angle = 20),
               position = position_attractsegment(start_shave = 0.15, 
                                                  end_shave = 0.15)) +
  xlim(c(0, 1)) +
  ylim(c(0, 1)) +
  theme_classic() + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=rel(1)),
        axis.title.x=element_blank(), 
        axis.text.x=element_text(size=rel(1)))
panel_B
```
## Panel C

No individualized gut microbiomes with a time dependent environmental response.

### Set up dataframes

Create two tibbles - one for the points and one for the arrows.

```{r df_c}
points_c = tibble(Individual = c("A", "A", "A", "A", "B", "B", 
                                 "B", "B", "C", "C", "C", "C"), 
                  Timepoint = c("1", "2", "3", "4", "1", "2", 
                                "3", "4", "1", "2", "3", "4"),
                  X = c(0.2, 0.45, 0.45, 0.225, 0.35, 0.6, 0.6, 0.375,
                        0.55, 0.8, 0.8, 0.575),
                  Y = c(0.2, 0.9, 0.4, 0.6, 0.8, 0.4, 0.2, 0.1, 
                        0.5, 0.7, 0.3, 0.9))
arrows_c = tibble(Individual = c("A", "A", "A", "B", "B", "B", "C", "C", "C"),
                  xstart = c(0.2, 0.45, 0.45, 0.35, 0.6, 0.6, 
                             0.55, 0.8, 0.8),
                  xend = c(0.45, 0.45, 0.225, 0.6, 0.6, 0.375, 
                           0.8, 0.8, 0.575),
                  ystart = c(0.2, 0.9, 0.4, 0.8, 0.4, 0.2, 0.5, 0.7, 0.3),
                  yend = c(0.9, 0.4, 0.6, 0.4, 0.2, 0.1, 0.7, 0.3, 0.9))
```

Create a scatterplot with arrows connecting points within the same individual. Color denotes individual and shape denotes timepoint.

```{r panel_c}
panel_C = ggplot(points_c) + 
  geom_point(aes(x = X, y = Y, color = Individual, shape = Timepoint), 
             size = 3) +
  scale_color_manual(values = c("#1ec93e", "#008ec8", "#4e3182")) +
  scale_shape_manual(values = c(15, 16, 17, 18)) +
  geom_segment(data = arrows_c, 
               aes(x = xstart, xend = xend, y = ystart, yend = yend,
                   color = Individual), 
               arrow = arrow(angle = 20),
               position = position_attractsegment(start_shave = 0.15, 
                                                  end_shave = 0.15)) +
  xlim(c(0, 1)) +
  ylim(c(0, 1)) +
  theme_classic() + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=rel(1)),
        axis.title.x=element_blank(), 
        axis.text.x=element_text(size=rel(1)))
panel_C
```

## Panel D

No individualized gut microbiomes without a time dependent environmental response.

### Set up dataframes

Create two tibbles - one for the points and one for the arrows.

```{r df_d}
points_d = tibble(Individual = c("A", "A", "A", "A", "B", "B", 
                                 "B", "B", "C", "C", "C", "C"), 
                  Timepoint = c("1", "2", "3", "4", "1", "2", 
                                "3", "4", "1", "2", "3", "4"),
                  X = c(0.2, 0.225, 0.45, 0.45, 0.35, 0.6, 0.375, 0.6,
                        0.55, 0.8, 0.8, 0.575),
                  Y = c(0.6, 0.2, 0.3, 0.9, 0.4, 0.8, 0.3, 0.15,
                        0.7, 0.8, 0.5, 0.3))
arrows_d = tibble(Individual = c("A", "A", "A", "B", "B", "B", "C", "C", "C"),
                  xstart = c(0.2, 0.225, 0.45, 0.35, 0.6, 0.375, 
                             0.55, 0.8, 0.8),
                  xend = c(0.225, 0.45, 0.45, 0.6, 0.375, 0.6, 
                           0.8, 0.8, 0.575),
                  ystart = c(0.6, 0.2, 0.3, 0.4, 0.8, 0.3, 0.7, 0.8, 0.5),
                  yend = c(0.2, 0.3, 0.9, 0.8, 0.3, 0.15, 0.8, 0.5, 0.3))
```

Create a scatterplot with arrows connecting points within the same individual. Color denotes individual and shape denotes timepoint.

```{r panel_d}
panel_D = ggplot(points_d) + 
  geom_point(aes(x = X, y = Y, color = Individual, shape = Timepoint), 
             size = 3) +
  scale_color_manual(values = c("#1ec93e", "#008ec8", "#4e3182")) +
  scale_shape_manual(values = c(15, 16, 17, 18)) +
  geom_segment(data = arrows_d, 
               aes(x = xstart, xend = xend, y = ystart, yend = yend,
                   color = Individual), 
               arrow = arrow(angle = 20),
               position = position_attractsegment(start_shave = 0.15, 
                                                  end_shave = 0.15)) +
  xlim(c(0, 1)) +
  ylim(c(0, 1)) +
  theme_classic() + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=rel(1)),
        axis.title.x=element_blank(), 
        axis.text.x=element_text(size=rel(1)))
panel_D
```

##
