---
title: "Graph code"
author: "EK Mallott"
date: "2022-09-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

This is code for the graphs for Mallott 2022 in Proc B.

## Workspace setup

The following packages are used for this analysis:
tidyverse 1.3.2
ggarchery 0.4.1
cowplot 1.1.1

```{r packages}
library(tidyverse)
library(ggarchery)
library(cowplot)
```

## Panel A

Individualized gut microbiomes with a time dependent environmental response.

### Set up dataframes

Create two tibbles - one for the points and one for the arrows.

```{r df_a}
points_a = tibble(Individual = c("A", "A", "A", "A", "B", "B", 
                                 "B", "B", "C", "C", "C", "C"), 
                  Timepoint = c("1", "2", "3", "4", "1", "2", 
                                "3", "4", "1", "2", "3", "4"),
                  MDS1 = c(0.2, 0.45, 0.45, 0.225, 0.35, 0.6, 0.6, 0.375,
                        0.55, 0.8, 0.8, 0.575),
                  MDS2 = c(0.2, 0.35, 0.15, 0.1, 0.75, 0.9, 0.7, 0.65,
                        0.4, 0.55, 0.35, 0.3))
arrows_a = tibble(Individual = c("A", "A", "A", "B", "B", "B", "C", "C", "C"),
                  xstart = c(0.2, 0.45, 0.45, 0.35, 0.6, 0.6, 
                             0.55, 0.8, 0.8),
                  xend = c(0.45, 0.45, 0.225, 0.6, 0.6, 0.375, 
                           0.8, 0.8, 0.575),
                  ystart = c(0.2, 0.35, 0.15, 0.75, 0.9, 0.7, 0.4, 0.55, 0.35),
                  yend = c(0.35, 0.15, 0.1, 0.9, 0.7, 0.65, 0.55, 0.35, 0.3))
```

Create a scatterplot with arrows connecting points within the same individual. Color denotes individual and shape denotes timepoint.

```{r panel_a}
panel_A = ggplot(points_a) + 
  geom_point(aes(x = MDS1, y = MDS2, color = Individual, shape = Timepoint), 
             size = 3) +
  scale_color_manual(values = c("#1ec93e", "#008ec8", "#4e3182")) +
  scale_shape_manual(values = c(15, 16, 17, 18)) +
  geom_arrowsegment(data = arrows_a, 
               aes(x = xstart, xend = xend, y = ystart, yend = yend,
                   color = Individual),
               arrows = arrow(length = unit(0.1, "inches")),
               position = position_attractsegment(start_shave = 0.035, 
                                                  end_shave = 0.035,
                                                  type_shave = "distance")) +
  xlim(c(0, 1)) +
  ylim(c(0, 1)) +
  theme_classic() + 
  theme(axis.title.y=element_text(size=rel(1.2)),
        axis.text.y=element_text(size=rel(1)),
        axis.title.x=element_text(size=rel(1.2)), 
        axis.text.x=element_text(size=rel(1))) +
  coord_fixed()
panel_A
```

## Panel B

Individualized gut microbiomes without a time dependent environmental response.

### Set up dataframes

Create two tibbles - one for the points and one for the arrows.

```{r df_b}
points_b = tibble(Individual = c("A", "A", "A", "A", "B", "B", 
                                 "B", "B", "C", "C", "C", "C"), 
                  Timepoint = c("1", "2", "3", "4", "1", "2", 
                                "3", "4", "1", "2", "3", "4"),
                  MDS1 = c(0.2, 0.225, 0.45, 0.45, 0.35, 0.6, 0.375, 0.6,
                        0.55, 0.8, 0.8, 0.575),
                  MDS2 = c(0.2, 0.1, 0.15, 0.35, 0.75, 0.7, 0.65, 0.9, 
                        0.4, 0.55, 0.35, 0.3))
arrows_b = tibble(Individual = c("A", "A", "A", "B", "B", "B", "C", "C", "C"),
                  xstart = c(0.2, 0.225, 0.45, 0.35, 0.6, 0.375, 
                             0.55, 0.8, 0.8),
                  xend = c(0.225, 0.45, 0.45, 0.6, 0.375, 0.6, 
                           0.8, 0.8, 0.575),
                  ystart = c(0.2, 0.1, 0.15, 0.75, 0.7, 0.65, 0.4, 0.55, 0.35),
                  yend = c(0.1, 0.15, 0.35, 0.7, 0.65, 0.9, 0.55, 0.35, 0.3))
```

Create a scatterplot with arrows connecting points within the same individual. Color denotes individual and shape denotes timepoint.

```{r panel_b}
panel_B = ggplot(points_b) + 
  geom_point(aes(x = MDS1, y = MDS2, color = Individual, shape = Timepoint), 
             size = 3) +
  scale_color_manual(values = c("#1ec93e", "#008ec8", "#4e3182")) +
  scale_shape_manual(values = c(15, 16, 17, 18)) +
  geom_arrowsegment(data = arrows_b, 
               aes(x = xstart, xend = xend, y = ystart, yend = yend,
                   color = Individual),
               arrows = arrow(length = unit(0.1, "inches")),
               position = position_attractsegment(start_shave = 0.035, 
                                                  end_shave = 0.035,
                                                  type_shave = "distance")) +
  xlim(c(0, 1)) +
  ylim(c(0, 1)) +
  theme_classic() + 
  theme(axis.title.y=element_text(size=rel(1.2)),
        axis.text.y=element_text(size=rel(1)),
        axis.title.x=element_text(size=rel(1.2)), 
        axis.text.x=element_text(size=rel(1))) +
  coord_fixed()
panel_B
```
## Panel C

No individualized gut microbiomes with a time dependent environmental response.

### Set up dataframes

Create two tibbles - one for the points and one for the arrows.

```{r df_c}
points_c = tibble(Individual = c("A", "A", "A", "A", "B", "B", 
                                 "B", "B", "C", "C", "C", "C"), 
                  Timepoint = c("1", "2", "3", "4", "1", "2", 
                                "3", "4", "1", "2", "3", "4"),
                  MDS1 = c(0.2, 0.45, 0.45, 0.225, 0.35, 0.6, 0.6, 0.375,
                        0.55, 0.8, 0.8, 0.575),
                  MDS2 = c(0.2, 0.9, 0.4, 0.6, 0.8, 0.4, 0.2, 0.1, 
                        0.5, 0.7, 0.3, 0.9))
arrows_c = tibble(Individual = c("A", "A", "A", "B", "B", "B", "C", "C", "C"),
                  xstart = c(0.2, 0.45, 0.45, 0.35, 0.6, 0.6, 
                             0.55, 0.8, 0.8),
                  xend = c(0.45, 0.45, 0.225, 0.6, 0.6, 0.375, 
                           0.8, 0.8, 0.575),
                  ystart = c(0.2, 0.9, 0.4, 0.8, 0.4, 0.2, 0.5, 0.7, 0.3),
                  yend = c(0.9, 0.4, 0.6, 0.4, 0.2, 0.1, 0.7, 0.3, 0.9))
```

Create a scatterplot with arrows connecting points within the same individual. Color denotes individual and shape denotes timepoint.

```{r panel_c}
panel_C = ggplot(points_c) + 
  geom_point(aes(x = MDS1, y = MDS2, color = Individual, shape = Timepoint), 
             size = 3) +
  scale_color_manual(values = c("#1ec93e", "#008ec8", "#4e3182")) +
  scale_shape_manual(values = c(15, 16, 17, 18)) +
  geom_arrowsegment(data = arrows_c, 
               aes(x = xstart, xend = xend, y = ystart, yend = yend,
                   color = Individual),
               arrows = arrow(length = unit(0.1, "inches")),
               position = position_attractsegment(start_shave = 0.035, 
                                                  end_shave = 0.035,
                                                  type_shave = "distance")) +
  xlim(c(0, 1)) +
  ylim(c(0, 1)) +
  theme_classic() + 
  theme(axis.title.y=element_text(size=rel(1.2)),
        axis.text.y=element_text(size=rel(1)),
        axis.title.x=element_text(size=rel(1.2)), 
        axis.text.x=element_text(size=rel(1))) +
  coord_fixed()
panel_C
```

## Panel D

No individualized gut microbiomes without a time dependent environmental response.

### Set up dataframes

Create two tibbles - one for the points and one for the arrows.

```{r df_d}
points_d = tibble(Individual = c("A", "A", "A", "A", "B", "B", 
                                 "B", "B", "C", "C", "C", "C"), 
                  Timepoint = c("1", "2", "3", "4", "1", "2", 
                                "3", "4", "1", "2", "3", "4"),
                  MDS1 = c(0.2, 0.225, 0.45, 0.45, 0.35, 0.6, 0.375, 0.6,
                        0.55, 0.8, 0.8, 0.575),
                  MDS2 = c(0.6, 0.2, 0.3, 0.9, 0.4, 0.8, 0.3, 0.15,
                        0.7, 0.8, 0.5, 0.3))
arrows_d = tibble(Individual = c("A", "A", "A", "B", "B", "B", "C", "C", "C"),
                  xstart = c(0.2, 0.225, 0.45, 0.35, 0.6, 0.375, 
                             0.55, 0.8, 0.8),
                  xend = c(0.225, 0.45, 0.45, 0.6, 0.375, 0.6, 
                           0.8, 0.8, 0.575),
                  ystart = c(0.6, 0.2, 0.3, 0.4, 0.8, 0.3, 0.7, 0.8, 0.5),
                  yend = c(0.2, 0.3, 0.9, 0.8, 0.3, 0.15, 0.8, 0.5, 0.3))
```

Create a scatterplot with arrows connecting points within the same individual. Color denotes individual and shape denotes timepoint.

```{r panel_d}
panel_D = ggplot(points_d) + 
  geom_point(aes(x = MDS1, y = MDS2, color = Individual, shape = Timepoint), 
             size = 3) +
  scale_color_manual(values = c("#1ec93e", "#008ec8", "#4e3182")) +
  scale_shape_manual(values = c(15, 16, 17, 18)) +
  geom_arrowsegment(data = arrows_d, 
               aes(x = xstart, xend = xend, y = ystart, yend = yend,
                   color = Individual),
               arrows = arrow(length = unit(0.1, "inches")),
               position = position_attractsegment(start_shave = 0.035, 
                                                  end_shave = 0.035,
                                                  type_shave = "distance")) +
  xlim(c(0, 1)) +
  ylim(c(0, 1)) +
  theme_classic() + 
  theme(axis.title.y=element_text(size=rel(1.2)),
        axis.text.y=element_text(size=rel(1)),
        axis.title.x=element_text(size=rel(1.2)), 
        axis.text.x=element_text(size=rel(1))) +
  coord_fixed()
panel_D
```

## Panel E

This graph shows the change in MDS1 over time for each individual where the gut microbiome responds similarly to environmental change in each individual.

```{r panel_e}
panel_E = ggplot(points_a, aes(x = Timepoint, y = MDS1, group = Individual)) +
  geom_line(aes(color = Individual)) +
  geom_point(aes(color = Individual)) + 
  scale_color_manual(values = c("#1ec93e", "#008ec8", "#4e3182")) +
  theme_classic() + 
  theme(axis.title.y=element_text(size=rel(1.2)),
        axis.text.y=element_text(size=rel(1)),
        axis.title.x=element_text(size=rel(1.2)), 
        axis.text.x=element_text(size=rel(1)))
panel_E
```
## Panel F

This graph shows the change in MDS1 over time for each individual where the gut microbiome does not respond similarly to environmental change in each individual.

```{r panel_f}
panel_F = ggplot(points_b, aes(x = Timepoint, y = MDS1, group = Individual)) +
  geom_line(aes(color = Individual)) +
  geom_point(aes(color = Individual)) + 
  scale_color_manual(values = c("#1ec93e", "#008ec8", "#4e3182")) +
  theme_classic() + 
  theme(axis.title.y=element_text(size=rel(1.2)),
        axis.text.y=element_text(size=rel(1)),
        axis.title.x=element_text(size=rel(1.2)), 
        axis.text.x=element_text(size=rel(1)))
panel_F
```

## Combined figure

All panels are stitched together into one figure.

```{r fig1}
legend = get_legend(panel_A)

tiff(file="fig1.tif", 
     res=300, width=8, height=10, units="in")
graphs = plot_grid(panel_A + theme(legend.position = "none"), 
                  panel_B + theme(legend.position = "none"), 
                  panel_C + theme(legend.position = "none"), 
                  panel_D + theme(legend.position = "none"), 
                  panel_E + theme(legend.position = "none"), 
                  panel_F + theme(legend.position = "none"), 
                  nrow = 3, ncol = 2, 
                  labels = c("A", "B", "C", "D", "E", "F"),
                  align = "hv")
plot1 = plot_grid(graphs, legend, nrow = 1, ncol = 2, rel_widths = c(0.9, 0.1))
dev.off()

setEPS()
postscript(file="fig1.eps", width=8, height=10, paper = "special")
plot1
dev.off()
```